Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/structureScene.tex
punctuation in introduction

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity researchers have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

@@

The wavelet transform of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelet filters
Applying pointwise complex modulus the transform yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t)\mbox{.}
\end{equation}
The scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q_1}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the temporal resolution of the traditional CQT is fixed by the support of the STFT analyzing window. %\cite{Brown1992}
Therefore, the scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost
since the inverse fast Fourier transform (IFFT) routine must be called for each wavelet $\boldsymbol{\psi_{\gamma_1}}$ in the filter bank. \ja{Is the cost really greater?}
However, this allows us to observe amplitude modulations at fine temporal scales in the scalogram, down to $2Q_1/\xi_1$ for $\gamma_1 = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$. \ja{Where does the formula $2Q_1/\xi_1$ come from?}

>>>>

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13b}. 
In addition, recent work has explored acoustic monitoring for characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound}, as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these applications are of considerable interest for the signal processing community.

@@

The wavelet transform of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelet filters
Applying pointwise complex modulus the transform yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t)\mbox{.}
\end{equation}
The scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q_1}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the temporal resolution of the traditional CQT is fixed by the support of the STFT analyzing window. %\cite{Brown1992}
Therefore, the scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost
since the inverse fast Fourier transform (IFFT) routine must be called for each wavelet $\boldsymbol{\psi_{\gamma_1}}$ in the filter bank. \ja{Is the cost really greater?}
However, this allows us to observe amplitude modulations at fine temporal scales in the scalogram, down to $2Q_1/\xi_1$ for $\gamma_1 = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$.
